---
title: "easytidymodels Regression Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{easytidymodels Regression Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Set up package and load in data for analysis

Generally, you want to set a seed so that your analysis is reproducible.

If easytidymodels isn't installed you can install it through devtools, which is on Github.

If you want to use the dataset provided here you will need to install modeldata.

Parallel computing is used through the doParallel library to speed up computations.

```{r setup, eval = FALSE}
set.seed(24)

# install.packages("devtools")
# devtools::install_github("amanda-park/easytidymodels")
library(easytidymodels)
library(recipes)
library(doParallel)

data(ames, package = "modeldata")

#Use parallel compute to speed up processing time
cores <- parallel::detectCores(logical = FALSE)
registerDoParallel(cores = cores)

```

## Prepare data for analysis with preprocessing

Define your response variable and save it as resp.

trainTestSplit is a wrapper for rsample's function to split your training and testing data. There is the option to split based on time dependency and to stratify on the response if you aren't splitting based on time.

recipes are your model's preprocessing steps. This varies for each data set you work with the level of preprocessing you need, so instead this portion of tidymodels has not been given a wrapper. The available preprocessing steps that you can use in recipes can be seen [here](https://recipes.tidymodels.org/reference/index.html).

After your recipe is set up, you can split your data into training and testing and then bake your recipe's preprocessing steps into the model.

Lastly, you can set up a cross-validation fold object through the function cvFolds.

These objects are all necessary for fitting the variety of models that tidymodels offers you.

```{r eval = FALSE}
#Define your response variable and formula object here
resp <- "Sale_Price"
formula <- stats::as.formula(paste(resp, ".", sep="~"))

#Split data into training and testing sets
split <- trainTestSplit(ames,
                        stratifyOnResponse = TRUE,
                        responseVar = resp)

#Create recipe for feature engineering for dataset, varies based on data working with
rec <- recipe(formula, data = split$train) %>%
  step_log(resp, base = 10) %>%
  step_YeoJohnson(Lot_Area, Gr_Liv_Area) %>%
  step_other(Neighborhood, threshold = .1)  %>%
  step_dummy(all_nominal()) %>%
  step_zv(all_predictors()) %>%
  step_nzv(all_predictors()) %>%
  step_corr(all_numeric(), -all_outcomes(), threshold = .8) %>%
  prep()

train_df <- bake(rec, split$train)
test_df <- bake(rec, split$test)

folds <- cvFolds(train_df)
```

# About all regression models

General workflow they all follow:

* Fit the model specified to training data
* Create a workflow and tune hyperparameters
* Choose optimal model based on evaluation metric chosen
* Evaluate model performance on training and testing data

Available evaluation metrics for evalMetric:

* [RMSE](https://yardstick.tidymodels.org/reference/rmse.html) (Root Mean Squared Error, call "rmse")
* [MAE](https://yardstick.tidymodels.org/reference/mae.html) (Mean Absolute Error, call "mae")
* [RSQ](https://yardstick.tidymodels.org/reference/rsq.html) (R-Squared, call "rsq")
* [MASE](https://yardstick.tidymodels.org/reference/mase.html) (Mean Absolute Scaled Error, call "mase")
* [CCC](https://yardstick.tidymodels.org/reference/ccc.html) (Concordance Correlation Coefficient, call "ccc")
* [IIC](https://yardstick.tidymodels.org/reference/iic.html) (Index of Ideality of Correlation, call "iic")
* [HUBER_LOSS](https://yardstick.tidymodels.org/reference/huber_loss.html) (Huber loss, call "huber_loss")

## Fit a KNN Model

Uses ``library(kknn)`` to compute model.

This is what the KNN model tunes:

* **neighbors**: The number of neighbors considered at each prediction.
* **weight_func**: The type of kernel function that weights the distances between samples.
* **dist_power**: The parameter used when calculating the Minkowski distance. This corresponds to the Manhattan distance with dist_power = 1 and the Euclidean distance with dist_power = 2.

```{r knn, eval = FALSE}
knnReg <- knnRegress(
  recipe = rec,
  response = resp,
  folds = folds,
  train = train_df,
  test = test_df,
  evalMetric = "rmse"
)

#Visualize training data and its predictions
knnReg$trainPred %>% select(.pred, !!resp)

#View how model metrics for RMSE, R-Squared, and MAE look for training data
knnReg$trainScore

#Visualize testing data and its predictions
knnReg$testPred %>% select(.pred, !!resp)

#View how model metrics for RMSE, R-Squared, and MAE look for testing data
knnReg$testScore

#See the final model chosen by KNN based on optimizing for your chosen evaluation metric
knnReg$final

#See how model fit looks based on another evaluation metric
knnReg$tune %>% tune::show_best("mae")
```

## Fit a Support Vector Machine (Radial Basis Kernel) Model

Uses ``library(kernlab)`` to compute SVM model.

What the model tunes:

* **cost**: The cost of predicting a sample within or on the wrong side of the margin.
* **rbf_sigma**: The precision parameter for the radial basis function.
* **margin**: The epsilon in the SVM insensitive loss function (regression only)

All the same evaluation methods for KNN are also available for SVM.

```{r eval = FALSE}
svmReg <- svmRegress(
  recipe = rec,
  response = resp,
  folds = folds,
  train = train_df,
  test = test_df,
  evalMetric = "rmse"
)

#Visualize training data and its predictions
svmReg$trainPred %>% select(.pred, !!resp)

#View how model metrics for RMSE, R-Squared, and MAE look for training data
svmReg$trainScore

#Visualize testing data and its predictions
svmReg$testPred %>% select(.pred, !!resp)

#View how model metrics for RMSE, R-Squared, and MAE look for testing data
svmReg$testScore

#See the final model chosen by svm based on optimizing for your chosen evaluation metric
svmReg$final

#See how model fit looks based on another evaluation metric
svmReg$tune %>% tune::show_best("mae")
```

## Fit a Tuned Linear Regression Model

Uses ``library(glmnet)`` to compute tuned linear regression model.

What the model tunes:

* **penalty**: The total amount of regularization in the model. Also known as lambda.
* **mixture**: The mixture amounts of different types of regularization (see below). If 1, amounts to LASSO regression. If 0, amounts to Ridge Regression. Also known as alpha.


```{r eval = FALSE}
linearReg <- linearRegress(
  recipe = rec,
  response = resp,
  folds = folds,
  train = train_df,
  test = test_df,
  evalMetric = "rmse",
  tidyModelVersion = TRUE
)

#Visualize training data and its predictions
linearReg$trainPred %>% select(.pred, !!resp)

#View how model metrics for RMSE, R-Squared, and MAE look for training data
linearReg$trainScore

#Visualize testing data and its predictions
linearReg$testPred %>% select(.pred, !!resp)

#View how model metrics for RMSE, R-Squared, and MAE look for testing data
linearReg$testScore

#See the final model chosen by linear based on optimizing for your chosen evaluation metric
linearReg$final

#See how model fit looks based on another evaluation metric
linearReg$tune %>% tune::show_best("mae")
```

## Fit a Random Forest Model

Uses ``library(ranger)`` to compute a random forest regression model.

What the model tunes:

* **mtry**: The number of predictors that will be randomly sampled at each split when creating the tree models.
* **min_n**: The minimum number of data points in a node that are required for the node to be split further.

What you set specifically:

* **trees**: Default is 100. Sets the number of trees contained in the ensemble. A larger values increases runtime but (ideally) leads to more robust outcomes.

```{r eval = FALSE}
rfReg <- rfRegress(
  recipe = rec,
  response = resp,
  folds = folds,
  train = train_df,
  test = test_df,
  calcFeatImp = TRUE,
  evalMetric = "mae"
)

#Visualize training data and its predictions
rfReg$trainPred %>% select(.pred, !!resp)

#View how model metrics for RMSE, R-Squared, and MAE look for training data
rfReg$trainScore

#Visualize testing data and its predictions
rfReg$testPred %>% select(.pred, !!resp)

#View how model metrics for RMSE, R-Squared, and MAE look for testing data
rfReg$testScore

#See the final model chosen by rf based on optimizing for your chosen evaluation metric
rfReg$final

#See how model fit looks based on another evaluation metric
rfReg$tune %>% tune::show_best("mae")

#See feature importance of model
rfReg$featImpPlot

#See numeric feature importance of model
rfReg$featImpVars
```

## Fit an XGBoost Model

Uses ``library(xgboost)`` to compute a random forest regression model.

What the model tunes:

* **mtry**: The number of predictors that will be randomly sampled at each split when creating the tree models.
* **min_n**: The minimum number of data points in a node that are required for the node to be split further.
* **tree_depth**: The maximum depth of the tree (i.e. number of splits).
* **learn_rate**: The rate at which the boosting algorithm adapts from iteration-to-iteration.
* **loss_reduction**: The reduction in the loss function required to split further.
* **sample_size**: The amount of data exposed to the fitting routine.

What you set specifically:

* **trees**: Default is 100. Sets the number of trees contained in the ensemble. A larger values increases runtime but (ideally) leads to more robust outcomes.

```{r eval = FALSE}
xgReg <- xgRegress(
  recipe = rec,
  response = resp,
  folds = folds,
  train = train_df,
  test = test_df,
  calcFeatImp = TRUE,
  evalMetric = "mae"
)

#Visualize training data and its predictions
xgReg$trainPred %>% select(.pred, !!resp)

#View how model metrics for RMSE, R-Squared, and MAE look for training data
xgReg$trainScore

#Visualize testing data and its predictions
xgReg$testPred %>% select(.pred, !!resp)

#View how model metrics for RMSE, R-Squared, and MAE look for testing data
xgReg$testScore

#See the final model chosen by xg based on optimizing for your chosen evaluation metric
xgReg$final

#See how model fit looks based on another evaluation metric
xgReg$tune %>% tune::select_best("rmse")

#See feature importance of model
xgReg$featImpPlot
```

## Fit a MARS Model

Uses ``library(earth)`` to compute a multi-adaptive regressive spline model.

What the model tunes:

* **num_terms**: The number of features that will be retained in the final model.
* **prod_degree**: The highest possible degree of interaction between features. A value of 1 indicates an additive model while a value of 2 allows, but does not guarantee, two-way interactions between features.
* **prune_method**: The type of pruning. Possible values are listed in ?earth.

```{r eval = FALSE}
marsReg <- marsRegress(
  recipe = rec,
  response = resp,
  folds = folds,
  train = train_df,
  test = test_df,
  evalMetric = "rmse"
)

#Visualize training data and its predictions
marsReg$trainPred %>% select(.pred, !!resp)

#View how model metrics for RMSE, R-Squared, and MAE look for training data
marsReg$trainScore

#Visualize testing data and its predictions
marsReg$testPred %>% select(.pred, !!resp)

#View how model metrics for RMSE, R-Squared, and MAE look for testing data
marsReg$testScore

#See the final model chosen by mars based on optimizing for your chosen evaluation metric
marsReg$final

#See how model fit looks based on another evaluation metric
marsReg$tune %>% tune::show_best("mae")
```

## Model Stacking Example

```{r eval = FALSE}
# Finalize parameters 

rfParam <- rfReg$tune %>% show_best("rmse", n=1) %>% 
  select(mtry, min_n)

xgParam <- xgReg$tune %>% 
  show_best("rmse", n=1) %>% 
  select(mtry:sample_size)

# Collect model predictions to stack

xgStack <- xgReg$tune %>% 
  collect_predictions() %>% 
  inner_join(xgParam) %>% 
  select(id, .row, !!resp, xgboost = .pred)

rfStack <- rfReg$tune %>% 
  collect_predictions() %>% 
  inner_join(rfParam) %>% 
  select(id, .row, randomforest = .pred)

marsStack <- marsReg$tune %>%
  collect_predictions() %>% 
  select(id, .row, mars = .pred)

knnStack <- knnReg$tune %>%
  collect_predictions() %>% 
  select(id, .row, knn = .pred)

svmStack <- svmReg$tune %>%
  collect_predictions() %>% 
  select(id, .row, svm = .pred)

lmStack <- linearReg$tune %>%
  collect_predictions() %>% 
  select(id, .row, lm = .pred)

stackDat <- xgStack %>% 
  left_join(rfStack) %>% 
  left_join(marsStack) %>%
  left_join(knnStack) %>%
  left_join(svmStack) %>%
  left_join(lmStack) %>%
  select(-id, -.row)

stackModel <- linear_reg(penalty = .2, mixture = 1) %>% 
  set_mode("regression") %>% 
  set_engine("glmnet") %>% 
  fit(formula, data = stackDat)

stackModel %>% tidy()

#Finalize model fits

xgFinal <- xgReg$final %>% last_fit(split$split)
rfFinal <- rfReg$final %>% last_fit(split$split)
marsFinal <- marsReg$final %>% last_fit(split$split)
knnFinal <- knnReg$final %>% last_fit(split$split)
svmFinal <- svmReg$final %>% last_fit(split$split)
lmFinal <- linearReg$final %>% last_fit(split$split)

stackFinal <- tibble("model" = list(xgFinal, rfFinal, marsFinal, knnFinal, svmFinal, lmFinal),
                         "model_names" = c("xgboost", "randomforest", "mars", "knn", "svm", "lm")) %>% 
  mutate(pred = map(model, collect_predictions))

stackFinal <- stackFinal %>% 
  select(model_names, pred) %>% 
  unnest(pred) %>% 
  pivot_wider(names_from = model_names, values_from = .pred) %>% 
  select(-id, -.row, -.config)

predict(stackModel, stackFinal) %>% 
  bind_cols(stackFinal) %>% 
  rename("stack" = .pred) %>% 
  pivot_longer(-!!resp) %>% 
  group_by(name) %>% 
  rmse(truth = !!resp, estimate = value) %>% 
  ungroup() %>% 
  pivot_wider(names_from = .metric, values_from = .estimate) %>% 
  arrange(rmse)
```
